\documentclass[]{font}


\begin{document}


\namesection{Anjan}{Das}{ \urlstyle{same}\url{http://www.anjandas.portfoliobox.net} \\
\href{mailto:dasanjan1296@gmail.com}{dasanjan1296@gmail.com} | \href{mailto:f2015150@pilani.bits-pilani.ac.in}{f2015150@pilani.bits-pilani.ac.in}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{BITS PILANI}
\descript{BE in Computer Science}
\location{Expected June 2019 | Pilani, India}
\sectionsep

\subsection{Deepika English \\ 
Medium School}
\descript{Intermediate in Science}
\location{Grad. May 2015|  Raurkela, India}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/dasanjan1296}{\custombold{dasanjan1296}} \\
LinkedIn://  \href{https://www.linkedin.com/in/dasanjan1296}{\custombold{dasanjan1296}} \\
YouTube://  \href{https://www.youtube.com/user/dasanjan1296}{\custombold{dasanjan1296}} \\
Twitter://  \href{https://twitter.com/dasanjan1296}{\custombold{@dasanjan1296}} \\
Quora://  \href{https://www.quora.com/anjan-das-6}{\custombold{anjan-das-6}}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}

\subsection{Undergraduate}
Information Retrieval \\
Operating Systems \\
Artificial Intelligence\\
Functional Programming \\
Machine Learning\\
{\footnotesize \textit{\textbf{(Research Asst. \& Teaching Asst) }}} \\
Compilers and Cool\\
Cryptography\\
Data Structures and Algorithms\\
Design and Analysis of Algorithms\\
High Speed Object Detection Algorithms\\
Computer Architecture\\
Unix Tools and Scripting \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Over 5000 lines:}
C \textbullet{} C++ \textbullet{} Java \textbullet{}   Shell \\
JavaScript \textbullet{} Matlab \textbullet{} Python \textbullet{} Rails\\  
\LaTeX\ \textbullet{} Git \textbullet{} Verilog HDL  \textbullet{} AUTOCAD\\ 
\location{Over 1000 lines:}
HTML5 \textbullet{} CSS \textbullet{} Mathematica \textbullet{} R \\
Assembly \textbullet{} Octave \textbullet{} Racket\\
\location{Familiar:}
Android \textbullet{} MySQL \textbullet{} C\#
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{CSIR - Central Electronics Engineering Research Institute}
\descript{| Research Intern }
\location{Jan 2017 – Present | Pilani, India}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Currently working under Scientist Mr. Pramod Kumar Tanwar, CEERI Pilani, in the field of Machine Learning on High Speed Vision Algorithms.
\end{tightemize}
\sectionsep

\runsubsection{North Eastern Space Application Centre}\\
\descript{| Summer Research Intern }
\location{May 2017 – Jul 2017 | Shillong, India}
\begin{tightemize}\item Developed a platform independent Auto-registration tool using GDAL, worked under Scientist Mr. Victor Saikhom and Scientist Mr. Siddhartha Bhuyan.
\end{tightemize}
\sectionsep

\runsubsection{BITS Pilani}
\descript{| Project Assistant }
\location{Jan 2017 – May 2017 | Pilani, India}
\begin{tightemize}
\item Worked under Dr. Kamlesh Tiwari, Assistant Professor, CSIS Dept., BITS Pilani, in the field of advanced object detection algorithms using Machine Learning.
\end{tightemize}
\sectionsep

\runsubsection{Project AMAL, AIESEC  Fes}
\descript{| Market Research Intern }
\location{Dec 2016 – Jan 2017 | Fes, Morocco}
\begin{tightemize}
\item Interned in a Moroccan based NGO, viz. Rotaract ENSA Fes, in the field of Marketing and helped improve their efficiency. 
\end{tightemize}
\sectionsep




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Research}
\runsubsection{ICBEMCONF 2017}
\descript{| Market Research}
\location{July 2017 | Moscow, Russia}
\begin{tightemize}
\item Invited for the ICBEMCONF-2017 held in Moscow to chair a session and presented a research paper on Company Valuation and Changing Paradigms.
\end{tightemize}
\sectionsep

\runsubsection{APOGEE BITS PILANI}
\descript{| Team Leader}
\location{Nov 2016 – Mar 2017 | Pilani, India}
\begin{tightemize}
\item Winner of the APOGEE 2017 Project Presentation for making an Android Application which detects blood Cholesterol levels right at home.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
\begin{tabular}{rll}
2017         & 1\textsuperscript{st}/40       & APOGEE-BITS Pilani\\
2017	     & 1\textsuperscript{st}/50 & Microsoft Coding Competition, BITS Pilani\\
2016         & 1\textsuperscript{st}/20 & Table Tennis Championship, BITS Pilani\\
2014	     & top 52/1021  & KVPY Fellowship\\
2011     & National & Indian Mathematics Olympiad (IMO) Finalist \\
2010     & National & Computer Society of India's National Programming Contest\\
\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXTRACURRICULAR ACTIVITIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Extra-curriculum}
Table Tennis \textbullet{} Badminton \textbullet{} Football \textbullet{} Chess
\textbullet{} Classical Guitar \textbullet{} Singing \\
Numismatics \textbullet{} Rubik's Cube \textbullet{} Travelling \textbullet{} Hiking \textbullet{} Running \textbullet{} Biking \\
Poetry  \textbullet{} Sketching \textbullet{} Reading \textbullet{} Volunteering
\sectionsep


\end{minipage} 
\end{document}